---
title: "Tanzania PbR Water Points Verification"
runtime: shiny
author: Jonathan
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    social: menu
    source_code: embed
    vertical_layout: fill
    storyboard: true
   
    
---

```{r setup, include=FALSE}
#Load the libraries that you will require
library(flexdashboard)
library(shiny)
library(dplyr)
library(plyr)
library(leaflet)
library(repmis)
library(tidyr)
library(htmltools)
library(tableHTML)
library(htmlTable)
library(rpivotTable)
library(descr)
library(tigerstats)
library(R2HTML)
```

```{r global, include=FALSE}

# load the Field verification dataset:
wpt_data_col <- read.csv('wpt_data.csv',header=TRUE)
# Load the sampled points dataset;
sample_points_wsg84 <- read.csv('ALLWSG84.csv',header=TRUE)
sample_points_1960 <- read.csv('ALL1960.csv',header=TRUE)

# Rename the OSM and Field Lat and Long to Lat and Long
wpt_data_col_osm <- rename(wpt_data_col,c("wpt.ctr.lat" = "lat", "wpt.ctr.lon" = "long"))
wpt_data_col_field <- rename(wpt_data_col,c("verified_wpts._wpt_gps_latitude" = "lat", "verified_wpts._wpt_gps_longitude" = "long"))

sample_points_wsg84 <- rename(sample_points_wsg84,c("LATITUDE" = "lat", "LONGITUDE" = "long"))
sample_points_1960 <- rename(sample_points_1960,c("LATITUDE" = "lat", "LONGITUDE" = "long"))

#Remove rows with NA in GPS in Field data
wpt_data_col_field <- wpt_data_col_field[!(is.na(wpt_data_col_field$verified_wpts.wpt_gps)),] 

```

Sidebar {.sidebar data-width=200}
=====================================
This drop down will show the LGAs that have been visited so far:

```{r}
# Create the LGAs dropdown list to use for filtering the data

selectInput("select", "Select an LGA:", choices = levels(wpt_data_col$wpt.LGA))

```

Overview {data-icon="fa-home"} 
=====================================  

Row {.tabset,orientation:columns}
-----------------------------------------------------------------------
### Completed Primary Sample: LGA (Level)

```{r}
renderValueBox({ # Call function to display a value box
  
  select <- reactive({
    input$select}) # Call the reactive select for the data in the value box
  
  wpt_omk_f <- wpt_data_col %>%
    filter(wpt_data_col$wpt.LGA==select()) # Filter the data based on the value selected
  
  sum_table <- sum(na.omit(wpt_omk_f$wpt.sample_colors) == "Primary_Sample") # Create a table
  
  valueBox(sum_table, 
           icon = "fa-tint",
           color = ifelse(sum_table >= 0, "orange", "primary")) # Create a value box from the table and assign params
})
```

### Completed Primary Replacement Sample: LGA (Level)

```{r}
renderValueBox({
  
  select <- reactive({
    input$select})
  
  wpt_omk_f <- wpt_data_col %>%
    filter(wpt_data_col$wpt.LGA==select())
  
  sum_table <- sum(na.omit(wpt_omk_f$wpt.sample_colors) == "Replacement_Sample")
  
  valueBox(sum_table, 
           icon = "fa-tint",
           color = ifelse(sum_table >= 0, "blue", "primary"))
})
```

### Completed Not in Sample Replacement: LGA (Level)

```{r}
renderValueBox({
  
  select <- reactive({
    input$select})
  
  wpt_omk_f <- wpt_data_col %>%
    filter(wpt_data_col$wpt.LGA==select())
  
  sum_table <- sum(na.omit(wpt_omk_f$wpt.sample_colors) == "Not_sample")
  
  valueBox(sum_table, 
           icon = "fa-tint",
           color = ifelse(sum_table >= 0, "grey", "primary"))
})
```

Column
-------------------------------------------------------------

### Table: A Table Output showing breakdown per village:

```{r}


renderTable ({ # Call function to display the output
  
  select <- reactive({
    input$select})
  
  wpt_omk_f <- wpt_data_col %>%
    filter(wpt_data_col$wpt.LGA==select())
  

summaryTable <- ddply(wpt_omk_f, "wpt.newvillage", summarise, 
          All_Completed = length(na.omit(wpt.sample_colors)),
          Primary_Sample=sum(na.omit(wpt.sample_colors == "Primary_Sample")),
          Replacement_Sample=sum(na.omit(wpt.sample_colors == "Replacement_Sample")),
          Not_Sample=sum(na.omit(wpt.sample_colors == "Not_sample")))

summaryTable

})

```

Map {data-icon="fa-globe"} 
===================================== 

### Field Map: Map showing visited Points based on Field Data, with an overlay of Sampled Points. **Green Points** with a **Blue Ring** around them are **Verified Points** from Field Data. __Orange__ = _Primary Sample_, __Blue__ = _Replacement Sample_, __Gray__ = _Other Points_: (Toggle to see the Sample Points, using the WSG84 Projection or the 1960 Projection.)


```{r}

# Create color scale

status_color <- colorFactor(c('grey','orange','blue'),domain = c('Not_sample','Primary_Sample','Replacement_Sample'))

# Create point size

size <- 5
    
    # Creating the Basemap
    
 tz_map <- 'https://api.mapbox.com/styles/v1/ona/ciuife06u00392inoja17ej74/tiles/256/{z}/{x}/{y}?access_token=pk.eyJ1Ijoib25hIiwiYSI6IlVYbkdyclkifQ.0Bz-QOOXZZK01dq4MuMImQ'
 
    
renderLeaflet({ # Call function to show the map
      
      select <- reactive({
    input$select})
  
  wpt_omk_f <- wpt_data_col_field %>%
    filter(wpt_data_col_field$wpt.LGA==select()) # Field data filter
  
  sample_data_f_wsg84 <- sample_points_wsg84 %>%
    filter(sample_points_wsg84$LGA==select()) # Sampled points WSG84 projection
  
    sample_data_f_1960 <- sample_points_1960 %>%
    filter(sample_points_1960$LGA==select())# Sampled points 1960 projection
  
      wpt_map <- leaflet(wpt_omk_f)%>% # Create the map using field data
        fitBounds(~min(long), ~min(lat), ~max(long), ~max(lat)) %>% # Set bounds
        
        addTiles(tz_map) %>% # Add the MapBox Basemap
        
        # Add the circle markers for the Field data
       addCircleMarkers(data=wpt_omk_f,lng = ~long, lat = ~lat, radius = size, fillColor = "green", 
                   popup = paste0(wpt_omk_f$wpt.newvillage,' || Count:',
                                  wpt_omk_f$wpt.newvillage), fillOpacity = 2.5, stroke = F)  %>% addCircleMarkers(
                                   clusterOptions = markerClusterOptions(),popup = ~htmlEscape(wpt_omk_f$wpt.WPTNAME))%>%
        
       # Add the circle markers for the sampled points WSG84 projection
         addCircleMarkers(data=sample_data_f_wsg84,group="Sample Points WSG84", radius = ~ size,color=~status_color(sample_colors),fill=TRUE,fillOpacity = 2.0,popup = ~htmlEscape(sample_data_f_wsg84$WPTNAME)) %>%
        
        # Add the circle markers for the sampled points 1960 projection
        addCircleMarkers(data=sample_data_f_1960,group="Sample Points 1960", radius = ~ size,color=~status_color(sample_colors),fill=TRUE,fillOpacity = 2.,popup = ~htmlEscape(sample_data_f_1960$WPTNAME)) %>%
        
        # Add the layer controls
        addLayersControl(
          baseGroups = c("Sample Points WSG84","Sample Points 1960"),
          options = layersControlOptions(collapsed = FALSE))
      
      
})
```

Indicators {data-icon="fa-bar-chart"} 
=====================================  

Row {.tabset,orientation:columns}
-----------------------------------------------------------------------


### Total Sampled Primary Points:

```{r}
renderValueBox({ # Call function to display a value box
  
  sum_table_primary_sampled <- sum(na.omit(sample_points_wsg84$sample_colors) == "Primary_Sample") # Create a table
  
  valueBox(sum_table_primary_sampled, 
           icon = "fa-tint",
           color = ifelse(sum_table_primary_sampled >= 0, "orange", "primary")) # Create a value box from the table and assign params
})
```

### Total Sampled Replacement Points:

```{r}
renderValueBox({ # Call function to display a value box
  
  sum_table_repl_sampled <- sum(na.omit(sample_points_wsg84$sample_colors) == "Replacement_Sample") # Create a table
  
  valueBox(sum_table_repl_sampled, 
           icon = "fa-tint",
           color = ifelse(sum_table_repl_sampled >= 0, "blue", "primary")) # Create a value box from the table and assign params
})
```

### Total Points not in Sample:

```{r}
renderValueBox({ # Call function to display a value box
  
  sum_table_non_sample <- sum(na.omit(sample_points_wsg84$sample_colors) == "Not_sample") # Create a table
  
  valueBox(sum_table_non_sample, 
           icon = "fa-tint",
           color = ifelse(sum_table_non_sample >= 0, "grey", "primary")) # Create a value box from the table and assign params
})
```

Row {.tabset,orientation:columns}
-------------------------------------
> Overall Progress:

### Overall Total number of **Completed** Water Points.

```{r}
renderValueBox({ # Call function to display a value box
  
  
  
  sum_table_total_Pry <- sum(na.omit(wpt_data_col$wpt.sample_colors) == "Primary_Sample")
  sum_table_total_Repl <- sum(na.omit(wpt_data_col$wpt.sample_colors) == "Replacement_Sample")
  sum_table_total_Not <- sum(na.omit(wpt_data_col$wpt.sample_colors) == "Not_sample")
  
 vTotal <- sum(sum_table_total_Pry,sum_table_total_Repl,sum_table_total_Not)
  
  valueBox(vTotal, 
           icon = "fa-tint",
           color = ifelse(vTotal >= 0, "green", "primary")) # Create a value box from the table and assign params
})
```

### Total number of **Remaining** Water Points.

```{r}
renderValueBox({ # Call function to display a value box
  
  
  pSample <- sum(na.omit(sample_points_wsg84$sample_colors) == "Primary_Sample")

  
  sum_table_total_Pry <- sum(na.omit(wpt_data_col$wpt.sample_colors) == "Primary_Sample")
  sum_table_total_Repl <- sum(na.omit(wpt_data_col$wpt.sample_colors) == "Replacement_Sample")
  sum_table_total_Not <- sum(na.omit(wpt_data_col$wpt.sample_colors) == "Not_sample")
  
 fTotal <- sum(sum_table_total_Pry,sum_table_total_Repl,sum_table_total_Not) 
  vRem <- pSample - fTotal
  
  valueBox(vRem, 
           icon = "fa-tint",
           color = ifelse(vRem >= 0, "red", "grey")) # Create a value box from the table and assign params
})
```

### Number of **Verified/ Found** Water Points.

```{r}
renderValueBox({ # Call function to display a value box
  
   sum_table_found <- sum(na.omit(wpt_data_col$osm_wp_verified) == "1")
 
  
  valueBox(sum_table_found, 
           icon = "fa-tint",
           color = ifelse(sum_table_found >= 0, "blue", "primary")) # Create a value box from the table and assign params
})
```

### % of the completed Water Points are **Verified/ Found:**

```{r}
renderValueBox({ # Call function to display a value box
  
  sum_table_total_Pry <- sum(na.omit(wpt_data_col$wpt.sample_colors) == "Primary_Sample")
  sum_table_total_Repl <- sum(na.omit(wpt_data_col$wpt.sample_colors) == "Replacement_Sample")
  sum_table_total_Not <- sum(na.omit(wpt_data_col$wpt.sample_colors) == "Not_sample")
  
 fTotal <- sum(sum_table_total_Pry,sum_table_total_Repl,sum_table_total_Not) 
  
   sum_table_found <- sum(na.omit(wpt_data_col$osm_wp_verified) == "1")
 
   pVerified <- round((sum_table_found / fTotal)*100)
  
  valueBox(pVerified, 
           icon = "fa-tint",
           color = ifelse(pVerified >= 0, "blue", "primary")) # Create a value box from the table and assign params
})
```

### Number of **Functional** Water Points.

```{r}
renderValueBox({ # Call function to display a value box
  
   sum_table_found_Func <- sum(na.omit(wpt_data_col$verified_wpts.wpt_current_functionality) == "1")
 
  
  valueBox(sum_table_found_Func, 
           icon = "fa-tint",
           color = ifelse(sum_table_found_Func >= 0, "blue", "primary")) # Create a value box from the table and assign params
})
```

### % of Water Points are **Functional**.

```{r}
renderValueBox({ # Call function to display a value box
  
  sum_table_found_Verified <- sum(na.omit(wpt_data_col$osm_wp_verified) == "1")
  
   sum_table_found_Func <- sum(na.omit(wpt_data_col$verified_wpts.wpt_current_functionality) == "1")
 
   Pfunctional <- round((sum_table_found_Func / sum_table_found_Verified)*100)
  
  valueBox(Pfunctional, 
           icon = "fa-tint",
           color = ifelse(Pfunctional >= 0, "blue", "primary")) # Create a value box from the table and assign params
})
```

Row {.tabset,orientation:columns}
-------------------------------------
> Functionality Match

### Overall Water Points Match by Functionality( Pbr Vs Field ):

```{r}

renderGauge({
  
  wpt_data_col$field_status <- ifelse(wpt_data_col$verified_wpts.wpt_current_functionality ==1, "Functional", "Not functional")
  
  wpt_data_col$status_match <- ifelse(wpt_data_col$field_status == wpt_data_col$wpt.STATUS, 1, 0)
  

sum_table_func_match <- round(sum(wpt_data_col$status_match,na.rm = TRUE)/sum(complete.cases(wpt_data_col$status_match))*100)


gauge(sum_table_func_match, min = 0, max = 100, symbol = '%', gaugeSectors(
    success = c(75, 100), warning = c(40, 74), danger = c(0, 39)
  ))

})
```

Tables {data-icon="fa-table"} 
=====================================  

Row {.tabset,orientation:columns}
-------------------------------------

### **Verified** Completed Points: **%**

```{r}

renderTable({

      wpt_data_col$field_status <- ifelse(wpt_data_col$verified_wpts.wpt_current_functionality ==1, "Functional", "Not functional")
  
  wpt_data_col$status_match <- ifelse(wpt_data_col$field_status == wpt_data_col$wpt.STATUS, "Matched", "Not Matched")
  sum_table_found <- sum(na.omit(wpt_data_col$osm_wp_verified) == "1")
  
   sum_table_total_Pry <- sum(na.omit(wpt_data_col$wpt.sample_colors) == "Primary_Sample")
  sum_table_total_Repl <- sum(na.omit(wpt_data_col$wpt.sample_colors) == "Replacement_Sample")
  sum_table_total_Not <- sum(na.omit(wpt_data_col$wpt.sample_colors) == "Not_sample")
  sampled_points <- sum(na.omit(sample_points_wsg84$sample_colors=="Primary_Sample"))
  
  
  
  summaryTable <- ddply(wpt_data_col, "wpt.LGA", summarise, 
          All_Field = length(na.omit(wpt.sample_colors)),
          Field_Found_Count=sum(na.omit(osm_wp_verified == "1")),
          Field_Not_Found_Count=sum(na.omit(osm_wp_verified == "0")),
          Field_Found_Perc= round((Field_Found_Count / All_Field)*100),
          Field_Found_Functional_Count=sum(na.omit(field_status=="Functional")),
          Field_Found_Not_Functional_Count=sum(na.omit(field_status=="Not functional")),
          Field_Found_Functional_Perc= round((Field_Found_Functional_Count / All_Field)*100),
          PbR_Functional_Count=sum(na.omit(wpt.wpt_status == "1")),
          PbR_Not_Functional_Count=sum(na.omit(wpt.wpt_status == "0")),
          PbR_Functional_Perc=round((PbR_Functional_Count / All_Field)*100),
          Field_Found_Status_Matched_PbR_Count=sum(na.omit(status_match=="Matched")),
          Field_Found_Status_NOT_Matched_PbR_Count=sum(na.omit(status_match=="Not Matched")),
          Field_Found_Status_Matched_PbR_Perc= round((Field_Found_Status_Matched_PbR_Count / All_Field)*100))
  
write.csv(summaryTable,file='summaryTable_export.csv',append=T,row.names = F,col.names = F)
  
  
  summaryTable
  
})

```
